Ecosystem functional response across precipitation extremes in a sagebrush steppe

### 2017-11-02 manuscript/usses_water_ms.tex
more on response letter

At any given site, the relationship between aboveground net primary
productivity (ANPP) and water availability (e.g., soil moisture) can be
characterized by regressing historical observations of ANPP on
observations of soil moisture. Fitted functional responses can then be
used to infer how ANPP may change under future precipitation regimes
\citep[e.g.,][]{Hsu2012}. A problem with this approach is that it
requires extrapolation if future precipitation falls outside outside the
historical range of variability \citep{Smith2011, Peters2012}. For
example, the soil moisture-ANPP relationship may be linear within the
historical range of interannual variation, but could saturate at higher
levels of soil moisture. In fact, saturating relationships are actually
common \citep{Hsu2012, Gherardi2015a}, perhaps because other resources,
like nitrogen, become more limiting in wet years than dry years. Failure
to accurately estimate the curvature of the soil moisture-ANPP
relationship will lead to over- or underprediction of ANNP under extreme
precipitation \citep{Peters2012}.

>>>>

At any given site, the relationship between aboveground net primary
productivity (ANPP) and water availability (e.g., soil moisture) can be
characterized by regressing historical observations of ANPP on
observations of soil moisture. Fitted functional responses can then be
used to infer how ANPP may change under future precipitation regimes
\citep[e.g.,][]{Hsu2012}. A problem with this approach is that it
requires extrapolation if future precipitation falls outside the
historical range of variability \citep{Smith2011, Peters2012}. For
example, the soil moisture-ANPP relationship may be linear within the
historical range of interannual variation, but could saturate at higher
levels of soil moisture. In fact, saturating relationships are actually
common \citep{Hsu2012, Gherardi2015a}, perhaps because other resources,
like nitrogen, become more limiting in wet years than dry years. Failure
to accurately estimate the curvature of the soil moisture-ANPP
relationship will lead to over- or underprediction of ANNP under extreme
precipitation \citep{Peters2012}.
